%        File: revise.tex
%     Created: Wed Oct 27 02:00 PM 2018 P
% Last Change: Wed Oct 27 02:00 PM 2018 P
%

%
% Copyright 2007, 2008, 2009 Elsevier Ltd
%
% This file is part of the 'Elsarticle Bundle'.
% ---------------------------------------------
%
% It may be distributed under the conditions of the LaTeX Project Public
% License, either version 1.2 of this license or (at your option) any
% later version.  The latest version of this license is in
%    http://www.latex-project.org/lppl.txt
% and version 1.2 or later is part of all distributions of LaTeX
% version 1999/12/01 or later.
%
% The list of all files belonging to the 'Elsarticle Bundle' is
% given in the file `manifest.txt'.
%

% Template article for Elsevier's document class `elsarticle'
% with numbered style bibliographic references
% SP 2008/03/01
%
%
%
% $Id: elsarticle-template-num.tex 4 2009-10-24 08:22:58Z rishi $
%
%
%\documentclass[preprint,12pt]{elsarticle}
\documentclass[answers,11pt]{exam}

% \documentclass[preprint,review,12pt]{elsarticle}

% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or 5p,twocolumn
% for a journal layout:
% \documentclass[final,1p,times]{elsarticle}
% \documentclass[final,1p,times,twocolumn]{elsarticle}
% \documentclass[final,3p,times]{elsarticle}
% \documentclass[final,3p,times,twocolumn]{elsarticle}
% \documentclass[final,5p,times]{elsarticle}
% \documentclass[final,5p,times,twocolumn]{elsarticle}

% if you use PostScript figures in your article
% use the graphics package for simple commands
% \usepackage{graphics}
% or use the graphicx package for more complicated commands
\usepackage{graphicx}
% or use the epsfig package if you prefer to use the old commands
% \usepackage{epsfig}

% The amssymb package provides various useful mathematical symbols
\usepackage{amssymb}
% The amsthm package provides extended theorem environments
% \usepackage{amsthm}
\usepackage{amsmath}

% The lineno packages adds line numbers. Start line numbering with
% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
% for the whole article with \linenumbers after \end{frontmatter}.
\usepackage{lineno}

% I like to be in control
\usepackage{placeins}

% natbib.sty is loaded by default. However, natbib options can be
% provided with \biboptions{...} command. Following options are
% valid:

%   round  -  round parentheses are used (default)
%   square -  square brackets are used   [option]
%   curly  -  curly braces are used      {option}
%   angle  -  angle brackets are used    <option>
%   semicolon  -  multiple citations separated by semi-colon
%   colon  - same as semicolon, an earlier confusion
%   comma  -  separated by comma
%   numbers-  selects numerical citations
%   super  -  numerical citations as superscripts
%   sort   -  sorts multiple citations according to order in ref. list
%   sort&compress   -  like sort, but also compresses numerical citations
%   compress - compresses without sorting
%
% \biboptions{comma,round}

% \biboptions{}


% Katy Huff addtions
\usepackage{xspace}
\usepackage{color}

\usepackage{multirow}
\usepackage[hyphens]{url}


\usepackage[acronym,toc]{glossaries}
\include{acros}

\makeglossaries

%\journal{Annals of Nuclear Energy}

\begin{document}

%\begin{frontmatter}

% Title, authors and addresses

% use the tnoteref command within \title for footnotes;
% use the tnotetext command for the associated footnote;
% use the fnref command within \author or \address for footnotes;
% use the fntext command for the associated footnote;
% use the corref command within \author for corresponding author footnotes;
% use the cortext command for the associated footnote;
% use the ead command for the email address,
% and the form \ead[url] for the home page:
%
% \title{Title\tnoteref{label1}}
% \tnotetext[label1]{}
% \author{Name\corref{cor1}\fnref{label2}}
% \ead{email address}
% \ead[url]{home page}
% \fntext[label2]{}
% \cortext[cor1]{}
% \address{Address\fnref{label3}}
% \fntext[label3]{}

\title{Neural Network Model Applciations to Reactor Fuel Depletion for Fuel Cycle Modeling\\
        \large Response to Review Comments}
\author{Jin Whan Bae, Andrei Rykhlevskii, Gwendolyn Chee, Kathryn D. Huff}

% use optional labels to link authors explicitly to addresses:
% \author[label1,label2]{<author name>}
% \address[label1]{<address>}
% \address[label2]{<address>}


%\author[uiuc]{Kathryn Huff}
%        \ead{kdhuff@illinois.edu}
%  \address[uiuc]{Department of Nuclear, Plasma, and Radiological Engineering,
%        118 Talbot Laboratory, MC 234, Universicy of Illinois at
%        Urbana-Champaign, Urbana, IL 61801}
%
% \end{frontmatter}
\maketitle
\section*{Review General Response}
Thank you for the thorough, careful review
[comment about test set]


\section*{Abstract}
\begin{questions}

        %---------------------------------------------------------------------
        \question Abstract. Motivation could appear somewhere

        \begin{solution}
        	Added:
            
            , to implement a quick, medium-fidelity method to
            estimate depleted \gls{PWR} fuel assembly composition in a fuel
            cycle simulator.
        \end{solution}

        \question
        This is the key mistake Meaningless if no test set was reserved

        \begin{solution}
         I re-trained the neural network with a 80-20 split, where:
         80 - training
            - this set goes through a 3 fold cross validation,
            - where 80 * (2/3) train, 80/3 val
            - for hyperparameter search (performance comparison)
         20 - test set reserved for final model

         The results are added to the paper. 

        \end{solution}

        \quesiton
        Not exactly proprietary..

        \begin{solution}
        I was told that the UNF-ST\&DARDS software is privately available
        in RSICC, and is planned to be publicly available in the upcoming
        months. For the data itself, it is only available through direct
        contact with Kaushik Banerjee.
        \end{solution}

        \question
        Sentence missing a word..


        \begin{solution}
        I'm not quite sure what word is missing. Is it the grammar?
        \end{solution}

\section*{Introduction}

        \question
        Blue highlights

        \begin{solution}
        I assume they are highlighted because they're passive.
        Let me know if that's not the case.
        \end{solution}

        \question
        Review is missing built-in spectral and other methods

        \begin{solution}

        \end{solution}

        \question
        Was this copy-pasted from elsewhere?

        \begin{solution}
        From my master's thesis. Should I change things around?
        \end{solution}


\section*{Methods}
        \question
        Maybe figure would be better than a list

        Perhaps this should be a separate step

        \begin{solution}

        \end{solution}

        \question
        Are hidden layers and nodes per layer "Hyper parameters"

        \begin{solution}
        To the best of my knowledge they are, I guess the type of 
        regression algorithm (linear regression, random forest etc.)
        could also be a hyper parameter. Let me know what you think
        about this definition.
        \end{solution}

        \question
        Rephrase. Recognize that the reactor params could be input
        values

        \begin{solution}
        added:
            Also, it should be noted that the reactor
            parameters could be input values to the neural network model.
        \end{solution}

        \question
        Say this in a more compleeing way.

        \begin{solution}
            I'm sorry I'm having a hard time reading the handwriting.
            Can you clarify what you want done here?
        \end{solution}

        \question
        But it is now accessible via RSICC right?

        \begin{solution}
            I checked the RSICC website but couldn't find it there,
            I will double check with the guys working on it to
            confirm the access status of the database
        \end{solution}

        \question
        Machine learning may actually benefit from more extreme data...

        \begin{solution}
            I originally used all the data but the results werent
            great, so I decided to filter them, and I saw a significant
            increase in performance. I don't think this model should
            do well in predicting outliers by sacrificing its performance
            for predicting modern enrichment/burnup assemblies.
        \end{solution}


        \question
        Cite this, explain it?

        \begin{solution}
            I feel like explaining it would make the paragraph too
            lengthy and unnecessary. 
        \end{solution}


        \question
        So then, is it really fair?

        \begin{solution}
            I do see your point, but I think it is the best
            option I have? What do you think?
        \end{solution}

        \question
        This is circular
        To demonstrate this, you need a test set

        \begin{solution}
        I did mention the test set, and that we set aside
        20 percent prior to any training.
        \end{solution}

        \question
        No one knows what the recipe reactor is

        \begin{solution}
            Changed sentence to 

            This sort of implementation can be done with
            a recipe-based approach for modeling reactor depletion
            if the user defines multiple
            output recipes. 
        \end{solution}


\section*{Results}
        \question
        Why choose this one?
        \begin{solution}
            These enrichment-burnup values are just picked
            from random,to show some examples of this prediction
            algorithm's performance. I handpicked some of them
            to show the spectrum of enrichment-burnup sets.
        \end{solution}

        \question
        Why not compare the whole thing?
        \begin{solution}
            that is done later in the paper,
        \end{solution}

        \question
        There maybe a more dense way to show this info
        \begin{solution}
            I tried grid plots (2 x 2) but they were hard to see,
            and the colors became indistinguishable if I used the 
            same colorbar for all plots

            I also was looking at 3d, but I decided that this
            was the clearest way to show this data. Let me know
            if you know of a good way!
        \end{solution}

        \question
        What does median assembly mean?

        \begin{solution}
        I rewrote the sentence for clarity:

            The median values for burnup and initial enrichment are
            $41,552$ MWd/MT and 3.85 (wt\%), respectively. 
        \end{solution}


        \question
        In part, this is because you are comparing median with
        mean.. right?

        \begin{solution}
        I am not sure if I understand the question,
        The recipe is the composition for an assembly with median
        enrichment and burnup. I am not comparing the recipe to
        any average value..? 
        \end{solution}

        \question
        How is this a smooth line?

        \begin{solution}
        I used Pyne to generate 100 points for every inventory,
        so that the lines look continuous.
        \end{solution}


        \question
        Is this in the archetype of the toolkit

        \begin{solution}
        It is in the archetype, using python eval().
        I don't think the toolkit exists.
        \end{solution}

        \question
        What do you mean enrichment burnup matrix?

        \begin{solution}
        the matrix would have an enrichment / burnup
        matrix for each assembly, with a shape (n\_batch, n\_assem per patch).
        \end{solution}

        \question
        Seems like something that could be fixed fairly easily..

        \begin{solution}
        It would be if the neural network model could predict EOC keff,
        but the model does not, since the keff data is not in the UDB.
        But it would be a nice function to have.
        \end{solution}

        \question
        Great. this should be a cyclus toolkit addition

        \begin{solution}
        I agree, and I made the issue in github.com/cyclus/cyclus.
        I think Greg is workin on it. It's easy to implement in
        python archetypes since it's a python function that evaluates
        function definition strings into floats every timestep. I am
        unsure how it can be implemented cyclus-wide.
        \end{solution}


\section*{Conclusion}
        \question
         wow..

        \begin{solution}
            Sorry you had to see my inner dialog. I am not sure
            if this should be in the paper, given that I am not really
            an authority in these matters, if that makes any sense. I thought
            it was too bullish(?) of me to suggest a direction for the
            nuclear science community. Let me know what you think of this
            paragraph.
        \end{solution}

        




        %---------------------------------------------------------------------
\end{questions}
\bibliographystyle{unsrt}
\bibliography{revise}
\end{document}

  %
  % End of file `elsarticle-template-num.tex'.
